### 2019-02-13 2-Chapters/5-Chapter/chapter5.tex
Ok for tex root
Okay for chapters and parts
Lots of macro were clean up, almost done for copy/paste of chapter 5 from my ALT 2018 paper
Added gold and other colors, for Chapter 5.
I still don't have correct references...

%!TEX root = ../thesis.tex

% First chapter begins here
\chapter{Multi-Player Multi-Armed Bandits}
\label{chapter:5}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/5-Chapter/Images/}}

@@

This chapter is basically a raw include from my paper ``Multi-Player Bandits Revisited'', see https://hal.inria.fr/hal-01629733

I also need to include additional simulations from the latest research articles, and discussions about the new works that took inspiration in our paper.

@@

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson

% First chapter begins here
\chapter{Multi-Player Multi-Armed Bandits Models}
\label{chapter:5}
\minitoc

Abstract for Chapter 5.

\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/5-Chapter/Images/}}
\graphicspath{{2-Chapters/5-Chapter/ALT_2018__MPBandits.git/figures/}}

@@

\TODOL{I also need to include additional simulations from the latest research articles, and discussions about the new works that took inspiration in our paper.}

% ----------------------------------------------------------------------------
\input{2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex}

@@

% ----------------------------------------------------------------------------
\input{2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex}
